On-the-fly Algorithms for GKAT Equivalences \thanks{Identify applicable funding agency here. If none, delete this.}

### 2025-01-20 main.tex
merge

@@

Finally, we present our equivalence-checking algorithm as~\cref{alg:bisim}, where we first check if one of \(s\) or \(u\) is known to be dead, if so we only need to check whether the other is dead, because of~\Cref{thm:greedy-bisim-one-dead}; otherwise, we will check the conditions in~\Cref{thm:recursive-construction}.
Because trace equivalence is an equivalence relation, therefore we can organize the previously explored states into equivalent classes using an efficient union-find structure, instead of a set of state pairs.
This union-find structure need to provide two functions: \(\Call{union}{$s, u$}\) unions the equivalence class of \(s\) and \(u\), whereas \(\Call{eq}{$s, u$}\) checks whether \(s\) and \(u\) is in the same equivalence class.

@@

\section{Implementation and Evaluation}
We implement our symbolic on-the-fly bisimulation algorithm~(\Cref{alg:symb-bisim}) in Rust along with derivative based~(\Cref{fig:derivatives-rules}) and Thompson's construction based~(\Cref{tab:symb-Thompson-construction}) algorithms for constructing symbolic GKAT coalgebras. The source code and benchmark suite is freely available in our repository \url{https://anonymous.4open.science/r/rust-gkat-071E}.

>>>>

\begin{corollary}\label{thm:max-bisim-is-max-greedy-bisim}
    Given two GKAT coalgebra \(S\) and \(U\), carrier of the maximal bisimulation \({≡} ⊆ S × U\) is also the carrier of maximal greedy bisimulation.
    We will abuse the notation \(≡\) to represent both the maximal bisimulation and maximal greedy bisimulation.
\end{corollary}

\begin{proof}
    Consider the GKAT coalgebra \(≡_d\) as generated in~\cref{thm:dead-construction-greedy-bisim}, then the carrier of \(≡_d\) and \(≡\) coincide, because \(≡\) already contains all the dead state pairs, by~\Cref{thm:bisim-between-dead}.
    Because the 
\end{proof}

@@

Finally, we present our equivalence-checking algorithm as~\cref{alg:bisim}, which are mostly checking the conditions in~\cref{thm:recursive-construction}.  
In the algorithm, we use the text ``implies'', ``iff'', ``and'' are logical operators that takes booleans (i.e. true or false) and return a boolean.
Similarly, \(\&\!\&\) is the logical and operation, which is the same as the the written ``and''. 
We opt to use \(\&\!\&\), instead of ``and'', to separate the conditions for clarity; formally \(\&\!\&\) is the same function as ``and'', but binds less tightly.

Intuitively, starting with the pair of state \((s, u)\), it will explore following \(δ_≈\) in~\cref{def:greedy-bisim}.

@@

\section{Implementation and Evaluation}\label{sec:implementation}
We implement our symbolic on-the-fly bisimulation algorithm~(\Cref{alg:symb-bisim}) in Rust along with derivative based~(\Cref{fig:derivatives-rules}) and Thompson's construction based~(\Cref{tab:symb-Thompson-construction}) algorithms for constructing symbolic GKAT coalgebras. The source code and benchmark suite is freely available in our repository \url{https://anonymous.4open.science/r/rust-gkat-071E}.
